---
title: "Untitled"
author: "Luis Ospina-Forero"
date: "02/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Stochastic Block model for bipartite graphs
A work around to generate a bipartite graph with different community structures in R/Python using SBM from the `igraph` package.

For python there is an equivalent function `SBM`<https://igraph.org/python/api/latest/igraph._igraph.GraphBase.html#SBM> other igraph functions <https://igraph.org/python/api/latest/igraph.Graph.html>, or the multilevel community detection <https://igraph.org/python/api/latest/igraph.Graph.html#community_multilevel>.

## How to use SBM to generate bipartite graphs with community structure.

Undirected and Unweighted Bipartite Network  with two communities and two modes (bipartite). 
```{r,message=FALSE}
require(igraph)

nv <- 100 #nodes
nc <- 2 #comm
nb <- 2 * nc #blocks

#Number of nodes in each community and mode.
Com1_Mod1_nv <- 20 #nodes in community 1 that belong to mode 1.
Com1_Mod2_nv <- 10
Com2_Mod1_nv <- 40
Com2_Mod2_nv <- 30
sizes  <-  c(Com1_Mod1_nv,Com1_Mod2_nv,Com2_Mod1_nv,Com2_Mod2_nv)

Com1p <- 0.4  #Probability  of connection between nodes in community one.
Com2p <- 0.4  #Probability  of connection between nodes in community two.
p <- 0.01 #General probability of connection  betwen nodes in differnt commmunities.

community_prob <- matrix(nrow=nb, ncol=nb,0)
rownames(community_prob) <- c("Com1_Mod1","Com1_Mod2","Com2_Mod1","Com2_Mod2")
colnames(community_prob) <- c("Com1_Mod1","Com1_Mod2","Com2_Mod1","Com2_Mod2")
community_prob[1,2] <-  Com1p
community_prob[3,4] <-  Com2p

community_prob[1,4] <-  p
community_prob[2,3] <-  p

community_prob <- (community_prob+t(community_prob))
```

The resulting probability of connection between nodes of different blocks
```{r}
community_prob
```


Generation of the graph via *sample_sbm*.
```{r}
bipG <- sample_sbm(nv,community_prob,sizes,directed = FALSE,loops = FALSE)

Modes <- c(rep(1,Com1_Mod1_nv),rep(2,Com1_Mod2_nv),rep(1,Com2_Mod1_nv),rep(2,Com2_Mod2_nv))
Coms <- c(rep(1,Com1_Mod1_nv+Com1_Mod2_nv),rep(2,Com2_Mod1_nv+Com2_Mod2_nv))

bipG
```


## Plotting accorrding to mode or community
Note that the nodes in the graph are ordered according the block order in `community_prob`, i.e. `c("Com1_Mod1","Com1_Mod2","Com2_Mod1","Com2_Mod2")`.


```{r,fig.dim=c(20,20)}
col<-c("red","blue")
Shape<- c("circle", "square")
plot(bipG,vertex.color= col[Coms], vertex.shape=Shape[Modes],vertex.size=8)

plot(bipG,vertex.color= col[Coms], vertex.shape=Shape[Modes],layout = layout_as_bipartite(bipG,types = Modes==1),edge.curve=TRUE,vertex.size=5,vertex.cex=1)

adj <- get.adjacency(bipG)

```

